---
title: "Developing Data Products Project Part 1"
author: "Hans-Joachim Kirlum"
date: "24. Mai 2015"
output: html_document
---

For the course project I use the "swiss" dataset of the "datasets" package. The documentation of this dataset you can find with ?swiss in R-Studio.

Here is the code for the ui.R file

```{r, eval=FALSE}
library(shiny)
shinyUI(pageWithSidebar(
headerPanel("Swiss Fertility and Socioeconomic Indicators (1888) Data"),
sidebarPanel(

    selectInput("mu", "Variable:",
                c("Agriculture" = "Agriculture",
                  "Examination" = "Examination",
                  "Education" = "Education"))   
    ),
mainPanel(
    plotOutput('myHist')
)
))
```

And here is the code for the server.R file

```{r, eval=FALSE}
library(shiny)
library(UsingR)
data(swiss)
shinyServer(
    function(input, output) {
        output$myHist <- renderPlot({
            mu <- input$mu
            x_data <- swiss[,mu]
            plot(x_data, swiss$Fertility, xlab=mu, ylab="Fertility",
                 col='lightblue',main='Fertility in dependency on agriculture, examination or education')
            mean <- mean(x_data)
            lines(c(mean, mean), c(0, 200),col="red",lwd=5)
        })
        
    }
)
```

In dependency of the input the values of the fertility were plotted and the red line shows the mean of it.

##Help file ?swiss

###Swiss Fertility and Socioeconomic Indicators (1888) Data

####Description

Standardized fertility measure and socio-economic indicators for each of 47 French-speaking provinces of Switzerland at about 1888.

####Usage

swiss

####Format

A data frame with 47 observations on 6 variables, each of which is in percent, i.e., in [0, 100].

- [,1]    Fertility	Ig, ‘common standardized fertility measure’
- [,2]	Agriculture	% of males involved in agriculture as occupation
- [,3]	Examination	% draftees receiving highest mark on army examination
- [,4]	Education	% education beyond primary school for draftees.
- [,5]	Catholic	% ‘catholic’ (as opposed to ‘protestant’).
- [,6]	Infant.Mortality	live births who live less than 1 year.


All variables but ‘Fertility’ give proportions of the population.

####Details

(paraphrasing Mosteller and Tukey):

Switzerland, in 1888, was entering a period known as the demographic transition; i.e., its fertility was beginning to fall from the high level typical of underdeveloped countries.

The data collected are for 47 French-speaking “provinces” at about 1888.

Here, all variables are scaled to [0, 100], where in the original, all but "Catholic" were scaled to [0, 1].

####Note

Files for all 182 districts in 1888 and other years have been available at https://opr.princeton.edu/archive/pefp/switz.aspx.

They state that variables Examination and Education are averages for 1887, 1888 and 1889.

####Source

Project “16P5”, pages 549–551 in

Mosteller, F. and Tukey, J. W. (1977) Data Analysis and Regression: A Second Course in Statistics. Addison-Wesley, Reading Mass.

indicating their source as “Data used by permission of Franice van de Walle. Office of Population Research, Princeton University, 1976. Unpublished data assembled under NICHD contract number No 1-HD-O-2077.”

####References

Becker, R. A., Chambers, J. M. and Wilks, A. R. (1988) The New S Language. Wadsworth & Brooks/Cole.



